---
title: "Tutorial in Week 5"
author: "CHOI JAE BIN A0244864W E0878509"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
# Global options for the RMarkdown document
knitr::opts_chunk$set(include = TRUE,
                      message = FALSE, warning = FALSE, 
                      fig.align = "center",  out.width = "80%")
```

## Question 1
### Question 1.1
Answer part 1.1 here.

```{r}
library(tidyverse)
library(readxl)
library(stringr)
library(lubridate)
qn1_1 = read.csv("../data/ges_sg.csv", na.strings = "na", stringsAsFactors = TRUE) %>%
select(-1)
glimpse(qn1_1)
```

### Question 1.2
Answer part 1.2 here.

```{r}
qn1_2 = qn1_1 %>%
filter(year == 2022)%>%
group_by(university)%>%
summarize(median_employment = median(employment_rate_overall, na.rm = TRUE)) %>%
arrange(desc(median_employment))
```

## Question 1.3
Answer part 1.3 here. 

```{r}
qn1_3 = qn1_1 %>%
  filter(year == 2022 & university == "National University of Singapore") %>%
  group_by(school) %>%
  summarise(val = median(gross_monthly_median, na.rm = TRUE)) %>%
  arrange(val)

par(mar = c(5, 10, 2, 2))

barplot(qn1_3$val, names.arg = qn1_3$school, horiz = TRUE, las = 1, 
        cex.axis = 0.7, cex.names = 0.7, border = NA,
        main = "Median gross income by school, 2022",
        xlab = "Median gross income (dollars)")

grid()
```

## Question 2
Answer part 2 here. 

```{r}
file_names = c("andreazhang_S13774_4717352_Week 4 ANDREA ZHANG.Rmd",
"chettyraj_S11993_4717353_wk4_RC.RMD",
"choclarence_S10609_4717354_tut_wk_4.RMD",
"surya_S10197_4717355_Surya.Rmd")

qn_2 = str_split_fixed(file_names, "_", 4) %>%
  data.frame() %>%
  
  rename(student_name = 1, student_id = 2, assignment_id = 3, actual_file_name = 4) %>%
  
  mutate(student_id = str_remove(student_id, "S"),
         student_id = as.numeric(student_id),
         assignment_id = as.numeric(assignment_id))
glimpse(qn_2)
```

## Requirement

+ Use Markdown to add text and explain your code/results where necessary.

+ Always knit your RMarkdown file (`.Rmd`) to ensure it **renders to HTML without any errors** before submission.

+ Save your `.Rmd` frequently and submit it according to the requirements outlined for each tutorial/assessment.