---
title: "Tutorial in Week 4"
author: "CHOI JAE BIN A0244864W"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
# Global options for the RMarkdown document
knitr::opts_chunk$set(include = TRUE,
                      message = FALSE, warning = FALSE, 
                      fig.align = "center",  out.width = "80%")
```

## Question 1

### Question 1.1

Answer:

```{r}
library(readxl)
excel_sheets("../data/tourist.xlsx")
qn1_1 <- read_excel("../data/tourist.xlsx", sheet = 1, range = "A10:G24")
print(qn1_1)
```

### Question 1.2

Answer part 1.2 here.

```{r}
qn1_2 <- qn1_1[qn1_1$`Data Series` != "15 Days & Over (Number)", ]
print(qn1_2)
```

### Question 1.3

Answer part 1.3 here.

```{r}
qn1_3 <- sum(qn1_2$`2023 Dec`)
print(paste("The total number of international visitors in December 2023 is", qn1_3))
```

### Question 1.4

Answer part 1.4 here.

```{r}
barplot(qn1_2$`2023 Dec`/1000,
        names.arg = c("0", "1", "2", "3", "4", "5", "6", "7", "8-10", "11-14", "15-29", "30-59", ">=60"),
        las = 2,
        col = "grey",
        main = "Tourists' Length of Stay in Dec 2023",
        ylab = "Number of Arrivals (in thousands)",
        xlab = "Length of Stay (days)")
```

## Question 2

### Question 2.1

Answer part 2.1 here.

```{r}
qn2_1 <- read_excel("../data/tourist_total.xlsx", sheet = 1, range = "A3:B15")
print(qn2_1)
```

### Question 2.2

Answer part 2.2 here.

```{r}
library(lubridate)
qn2_1$Month = ym(qn2_1$Month)
print(qn2_1)
```

### Question 2.2

Answer part 2.2 here.

```{r}
plot(x = qn2_1$Month, y = qn2_1$Total/1000, type = "b",
     main = "Monthly tourist arrivals in 2023",
     xlab = "Month",
     ylab = "Number of arrivals (in thousands)")
```


## Requirement

-   Use Markdown to add text and explain your code/results where necessary.

-   Always knit your RMarkdown file (`.Rmd`) to ensure it **renders to HTML without any errors** before submission.

-   Save your `.Rmd` frequently and submit it according to the requirements outlined for each tutorial/assessment.
