---
title: "Tutorial in Week 6"
author: "CHOI JAE BIN A0244864W E0878509"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
# Global options for the RMarkdown document
knitr::opts_chunk$set(include = TRUE,
                      message = FALSE, warning = FALSE, 
                      fig.align = "center",  out.width = "80%")
```

## Question 1
### Question 1.1
Answer part 1.1 here.

```{r}
library(tidyverse)
library(readxl)
library(stringr)
library(lubridate)
qn1_1 = read_excel("../data/MSPUS.xls", skip = 10) %>%
  rename(date = 1, price = 2) %>%
  mutate(date = ymd(date)) 
```

### Question 1.2
Answer part 1.2 here.

```{r}
plot(x = qn1_1$date, 
     y = qn1_1$price/1000, 
     type = "l", 
     main = "Quarterly median house prices in the United States", 
     xlab = "Year", 
     ylab = "Median house prices (thousands)",
     las = 1,
     lwd = 3)
grid()
```

## Question 1.3
Answer part 1.3 here. 

```{r}
qn1_3 = qn1_1 %>% filter(date >= "2019-01-01", date <= "2024-09-01") %>%
  mutate(year = year(date), quarter = factor(str_c("Q", quarter(date))))
```

## Question 2.1
Answer part 2.1 here. 

```{r}
qn2_1 = read_excel("../data/tourist.xlsx", range = "A10:G24") %>%
  slice(-11) %>%
  rename(duration = 1) %>%
  mutate(k = row_number()) %>%
  pivot_longer(cols = 2:7,
               names_to = "date",
               values_to = "arrivals") %>%
  mutate(date = ym(date),
         month = month(date),
         year = year(date)) %>%
  select(k, duration, month, arrivals, date, year) %>%
  arrange(date)
glimpse(qn2_1)

```

## Question 2.2
Answer part 2.2 here. 

```{r}
qn2_2 = qn2_1 %>% group_by(month) %>%
  summarise(total = sum(arrivals))
```

## Question 2.3
Answer part 2.3 here. 

```{r}
qn2_3 = qn2_1 %>%
  group_by(duration) %>%
  mutate(rate = (arrivals - lag(arrivals))/lag(arrivals) * 100 ) %>%
  ungroup()%>%
  filter(!is.na(rate))
glimpse(qn2_3 %>% arrange(year, k))
```

## Requirement

+ Use Markdown to add text and explain your code/results where necessary.

+ Always knit your RMarkdown file (`.Rmd`) to ensure it **renders to HTML without any errors** before submission.

+ Save your `.Rmd` frequently and submit it according to the requirements outlined for each tutorial/assessment.